Data Pre-Processing

### 2021-06-08 AST-Framing-Ontario/Data Pre-Processesing.rmd
Split Procedure
Creation of corpus now pulls from clean texts as opposed trimmed ones

```{r}
pdfLocation <- params$Academic_Papers_SinglCol

@@

# Creates uniquely id text store in 'Environment'
assign(paste("text", n, sep = ""), readChar(newFile, file.info(newFile)$size))

@@

@@

Next, convert the data frame to a corpus:
```{r}
df_source <- DataframeSource(textDF)
corpus <- VCorpus(df_source)
# Example 
content(corpus[[2]])
```

@@

# Example
content(corpus[[2]])
```

>>>>

```{r}
pdfLocation <- params$Academic_Papers_DoubCol

@@

@@

## Creating importing texts to environment

imports texts that were manually cleaned

```{r}
# location of manually cleaned .txt documents
cleantxtLocation <- "Cleaned .txt/Academic Papers"

cleantxtlist <- list.files(cleantxtLocation, pattern = "*.txt", full.names=TRUE)
n <- 1 
for (txt in cleantxtlist) {

# Creates uniquely id text store in 'Environment'
assign(paste("text", n, sep = ""), readChar(txt, file.info(txt)$size))
n <- n + 1 
}
```

@@

Next, convert the data frame to a corpus:
```{r}
df_source <- DataframeSource(textDF)
corpus <- VCorpus(df_source)
# Example 
content(corpus[[6]])
```

@@

# Example
content(corpus[[6]])
```
